---
title: "Homework05"
author: "Alyssa Neuhaus"
date: "2/12/2020"
output: html_document
---
# Question 1:

Assign to the variable n_dims a single random integer between 3 and 10:
```{r}
n_dims <- sample(3:10, 1)
print(n_dims)
```

Create a vector of consequtive integers from 1 to n_dims^2:
```{r}
vec <- c(1:(n_dims)^{2})
print(vec)
```

Use the sample function to randomly reshuffle these values:
```{r}
sample(vec,((n_dims)^{2}))
```

Create a square matrix with these elements:
```{r}
m <-matrix(vec, nrow=n_dims, ncol=n_dims)
```

Print matrix:
```{r}
print(m)
```

Find function in r to transpose the matrix:
```{r}
m2 <- t(m)
```

Print transposed matrix:
```{r}
print(m2)
```
Matrix is now filled from left to right rather than from up to down. 

Calculate the sum and the mean of the element in the first row and the last row:
```{r}
FirstAndLastSum <-sum((m[,1]),(m[n_dims,]))
FirstAndLastSum

FirstAndLastMean <- FirstAndLastSum/n_dims
FirstAndLastMean
```

Use the eigen() function in matrix
```{r}
e <- eigen(m)
print(e)
```
The $values are exponential numbers, and the $vectors are decimels less than one. 

Figure out type:
```{r}
typeof(e$values)
```
```{r}
typeof(e$vectors)
```

# Question 2. 
Create a 4x4 matrix with random uniform numbers:
```{r}
my_matrix <- matrix(data=runif(16),
                    nrow=4,ncol=4)
print(my_matrix)
```

Set up a vector of random values and then apply an inequality to it:
```{r}
my_logical01 <- runif(100)
my_logical <- runif(100) < 0.5
print(my_logical)
```

26-element vector of all lower case letters in random order
```{r}
my_letters <- letters
my_letters <- sample(my_letters)
print(my_letters)
```

Create new list, which has the element [2,2] from the matrix, the second element of the logical vector, and the second element of the letters vector
```{r}
newList <- c(m[2,2],my_logical[2],my_letters[2])
print(newList)
```

Use typeof() function to confirm the underlying data types of each component in this list:
```{r}
i <- typeof(m)
print(i)
```

```{r}
l <-typeof(my_logical)
print(l)
```

```{r}
c <-typeof(my_letters)
print(c)
```

Combine underlying elements from new list into single atomic vector:
```{r}
elements <- c(i,l,c)
print(elements)
```

What is the data type of this vector?
```{r}
typeof(elements)
```

# Question 3. 

Create a data frame with two variables and 26 cases:
```{r}
my_unis <- runif(26, min=0, max=10)
my_letters <- sample(LETTERS)
d_frame <- data.frame(my_unis,my_letters,stringsAsFactors = FALSE)
print(d_frame)
```

For the first variable, use a single line of code in R to select 4 random rows and replace the numerical values in those rows with NA
```{r} 
d_frame[sample(x=length(my_unis),size=4),1] <- NA
print(d_frame)
```

For the first variable, write a single line of R code to identify which rows have the missing values:
```{r}
which(!complete.cases(d_frame$my_unis))
```

For the second variable, sort it in alphabetical order:
```{r}
d_frame[order(d_frame$my_letters),]
```

Calculate the column mean for the first variable: 
```{r}
mean(my_unis)
```






